Legends for supplementary material

### 2019-02-28 Manuscript/Supplementary/supplementary_legends.Rmd
legends edits

>>>>

**Supplementary Figure 2. Correlations between genomic annotations across cell lines and resolutions.** Lower triangular correlation heatmaps between genomic annotations for 10 kb (A), 25 kb (B), 50 kb (C), and 100 kb (D) data resolutions across the GM12878 (left column) and K562 (right column) cell lines. The correlations were based on the total number of overlapped bases between flanked TAD boundaries and genomic annotations. High correlations (red) denote annotations that tended to occur colocally near TAD boundaries. Low correlations (blue) denote annotations that did not tend to occur near TAD boundaries together.
